Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
patch application operator 改为斜体

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers (see Algorithm 1).
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with a shift range of 64 pixels, where shift is defined as the max range of translation generated by a uniform distribution.
%an offset $(\Delta_x, \Delta_y)$.
%We set this offset to $(\pm 64, \pm 64)$. 
%$\Delta_x$ (as well as $\Delta_y$) is randomly selected between -64 pixels and 64 pixels.
The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.

>>>>

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers (see Algorithm 1).
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with a shift range of 64 pixels, where shift is defined as the max range of translation generated by a uniform distribution.
The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is \textit{patch application operator} \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.
